Human Factors Influencing Visual Statistical Inference

### 2013-06-07 sociology_paper.tex
edited experiment setup

\section{Simulation Experiment and Methods}\label{sec:exp_design}
The performance of the observer while evaluating a lineup would depend on the factors described in Section \ref{sec:factor_performance}. This section presents the experimental setup, data collection methods and data analysis plans with models to asses the influence of those demographic factors on visual statistical inference.

\subsection{Experiment Setup}  In addition to the evaluation response of the lineup, all the 10 experiments shown in Table \ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:

>>>>

\section{Simulation Experiment and Methods}\label{sec:exp_design}
The performance of the observer while evaluating a lineup would depend on the factors described in Section \ref{sec:factor_performance}. This section presents the simulation experimental setup, data collection methods and data analysis plans with models to asses the influence of those factors on visual statistical inference.

\subsection{Experiment Setup}  In addition to obtain evaluation responses of the lineups, all the 10 experiments shown in Table \ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:
